The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2019-12-18 paper.tex
Updated Inayoshi references

How common are mergers of massive black holes?  For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}, \citet{2018ApJ...863L..36I}).  However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).  So, what does happen?  One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple orbiting black holes, which will eject a non-negligible fraction of the mass, may solve this problem.  The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.  What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and some of the orbiting ones might be detectable via their ability to accrete gas and emit radiation.

@@

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019arXiv190202349I}:
\begin{equation}
    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.

>>>>

How common are mergers of massive black holes?  For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018MNRAS.479.4017I}, \citet{2018ApJ...863L..36I}).  However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).  So, what does happen?  One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple orbiting black holes, which will eject a non-negligible fraction of the mass, may solve this problem.  The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.  What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and some of the orbiting ones might be detectable via their ability to accrete gas and emit radiation.

@@

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
\begin{equation}
    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
